---
title: "nascar.data"
format: html
---

An exploration of the [nascar.data](https://azimuth-project.tech/nascaR.data/index.html) package.

## Setup

```{r}
#| label: setup
#| message: false
#| warning: false

library(tidyverse)
library(janitor)
library(nascaR.data)
```


## Data functions

### Cup Series


```{r}
cup_series |> glimpse()
```

```{r}
cup_series |> head()
```


### Xfinity Series

```{r}
xfinity_series |> glimpse()
```

### Truck Series

```{r}
truck_series
```


## Info functions

### Driver

```{r}
get_driver_info("Kyle Busch", series = "all", type = "summary")
```


### Team

```{r}
get_team_info("Joe Gibbs Racing", series = "truck", type = "season")
```


### Manufacturer

```{r}
get_manufacturer_info("Chevrolet", series = "truck", type = "season")
```

## Let's look at a race

First, let's get the 2024 Cup Season

```{r}
c2024 <- cup_series |> clean_names() |> filter(season == 2024)
```


A look at the races, tracks

```{r}
c2024 |> 
  count(race, track)
```

And a single race. What do we get?

```{r}
c2024 |> 
  filter(race == 1)
```

## Prompt ideas

- how does start position affect finish?
- who might have led the fewest laps before winning?
- who has been in the most crashes?
- What is the average finish by make?
- Who is the best road racer?
- Who might be the best driver in multiple series?
- What is the rating?
- Which team has been most successful?
    - How do you even measure that?
