---
title: "FBref scores & schedules"
---

The aim is to pull data from a page like this: [2023 Scores and Fixtures](https://fbref.com/en/comps/22/2023/schedule/2023-Major-League-Soccer-Scores-and-Fixtures)

this uses the [worldfootballr package](https://jaseziv.github.io/worldfootballR/index.html) and mainly the [fb_match_results](https://jaseziv.github.io/worldfootballR/reference/fb_match_results.html)


- Figure out how to get one year
- Figure out how to save to computer
- Figure out how to do multiple years


## Setup

```{r}
#| label: setup
#| message: false
#| warning: false

library(tidyverse)
library(janitor)
library(worldfootballR)
```


## Match results function

This is our jam.


Match results

```{r}
mls_2024 <- fb_match_results(
  country = "USA",
  gender = "M",
  season_end_year = 2023,
  tier = "1st"
) |> clean_names()

mls_2024
```

## Austin sellout?

Interestingly, there is no Attendance reported for the final Austin FC home game in 2024.

```{r}
mls_2024 |> 
  filter(home == "Austin")
```

```{r}
mls_2024 |> filter(is.na(attendance), round == "Regular Season") |> 
  select(round, wk, date, home, away, attendance, venue) |> 
  arrange(date)
```













